Wilcoxon results tables - text and appendix

### 2017-12-15 analyses/03-statistical-analyses.Rmd
Minor tidying of code

---
title: "Outputs from time slice analyses"
author: "Natalie Cooper and Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 6
    fig_height: 6
---

This code runs the output analyses in the paper, i.e. creates tables and performs statistical tests.

@@

This script requires the outputs from `02-time-slice-analyses.Rmd`. This of course can all be written into functions but we ran out of time so here is some suboptimal but working code!

@@

#out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))
out1 <- readRDS(file = paste0("../outputs/epoch.", slug, ".Rda"))

@@

# Save outputs
outputS <- rbind(tidy(w_acc), tidy(w_del), tidy(w_grad), tidy(w_prox), 
                tidy(w_punc), tidy(w_rand))
outputS$model <- c("acctran", "deltran", "gradual.split", "proximity", 
                        "equal.split", "random")
outputS$type <- rep("stratigraphy", 6)
outputS$period <- rep(strat$stratigraphy[1], 6)

@@

Extinction effect
------------------

Here we can test the effect of mass extinction on the different methods with the different models (for each dataset!).
The way to test the extinction effect is a referential wilcoxon test.#' @param as.list \code{logical}, whether to output the results as a list for \code{\link{test.dispRity}} (\code{TRUE}) or not (\code{FALSE} - default).

In other words, we compare the bins/slice just before the extinction event to the three ones just after (to account for an eventual lag effect).

>>>>

---
title: "Statistical analyses of time slice outputs"
author: "Natalie Cooper and Thomas Guillerme"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 6
    fig_height: 6
---

This code runs the output analyses in the paper, i.e. performs statistical tests.

@@

This script requires the outputs from `02-time-slice-analyses.Rmd` and functions in `stats_fun.R`. This of course can all be written into functions but we ran out of time so here is some suboptimal but working code!

@@

out1 <- readRDS(file = paste0("../outputs/age.", slug, ".Rda"))
#out1 <- readRDS(file = paste0("../outputs/epoch.", slug, ".Rda"))

@@

# Save outputs
outputS <- rbind(tidy(w_acc), tidy(w_del), tidy(w_grad), tidy(w_prox), 
                tidy(w_punc), tidy(w_rand))
# Add model names
outputS$model <- c("acctran", "deltran", "gradual.split", "proximity", 
                        "equal.split", "random")
# Add that this is the stratigraphy method
outputS$type <- rep("stratigraphy", 6)
# Add label for "Age" vs. "Epoch"
outputS$period <- rep(strat$stratigraphy[1], 6)

@@

Mass extinction effects
---------------------

Here we can test the effect of mass extinction on the different methods with the different models (for each dataset).
The way to test the extinction effect is a referential wilcoxon test.#' @param as.list \code{logical}, whether to output the results as a list for \code{\link{test.dispRity}} (\code{TRUE}) or not (\code{FALSE} - default).

In other words, we compare the bins/slice just before the extinction event to the three ones just after (to account for an possible lag effect).

### 2017-12-15 analyses/05-figure-dtt.Rmd
Minor tidying of code

---
title: "Disparity through time - simplified and for appendix"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

pdf("../manuscript/figures/fig-dtt-age.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25),"points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25),"points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5),"points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos=list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

>>>>

---
title: "Disparity through time figures"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

Load packages

@@

pdf("../manuscript/figures/fig-dtt-age.pdf")  
  multiplot(beck_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25), "points")),
            brusatte_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25), "points")), 
            bapst_s + theme(plot.margin=unit(c(5.5, 5.5, 5.5, 25), "points")),
            wright_s + theme(plot.margin=unit(c(5.5, 5.5, 12, 25), "points")), 
            beck_d, brusatte_d, bapst_d, 
            wright_d + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5), "points")),
            beck_n,
            brusatte_n,
            bapst_n,
            wright_n + theme(plot.margin=unit(c(5.5, 5.5, 12, 5.5), "points")),
            cols = 3, 
            labs = list("Time (MYA)", 
                        "Relative disparity"),
            labpos = list(c(0.5, 0.015), c(0.03, 0.5)))
dev.off()
```

### 2017-12-15 analyses/06-table-wilcox.Rmd
Minor tidying of code

```{r}
# Stick p values and W values together
# Repalce p values with *
p.values.function <- function(data){ 
  for (i in 1:length(data$V2)){
    if(data$V2[i] < 0.05 & data$V2[i] > 0.01){data$V2[i] <- "*"}
    if(data$V2[i] < 0.01 & data$V2[i] > 0.001){data$V2[i] <- "**"}
    if(data$V2[i] < 0.001){data$V2[i] <- "***"}
    if(data$V2[i] > 0.05){data$V2[i] <- ""}
  }
  data$V6 <- paste0(data$V1, data$V2)
return(data)
}

@@

sink(file = "../manuscript/tables/raw_wilcox.tex")
print(xtable(table_out, caption = table_caption), include.rownames = FALSE)
sink()
```

@@

sink(file = "../manuscript/tables/raw_wilcox_appendix.tex")
print(xtable(table_out, caption = table_caption), include.rownames = FALSE)
sink()
```

>>>>

```{r}
# Stick p values and W values together
# Replace p values with *
p.values.function <- function(data){ 
  for (i in 1:length(data$V2)){
    if(data$V2[i] < 0.05 & data$V2[i] > 0.01){data$V2[i] <- "*"}
    if(data$V2[i] < 0.01 & data$V2[i] > 0.001){data$V2[i] <- "**"}
    if(data$V2[i] < 0.001){data$V2[i] <- "***"}
    if(data$V2[i] > 0.05){data$V2[i] <- ""}
  }
  data$V6 <- paste0(data$V1, data$V2)
return(data)
}

@@

## Save
sink(file = "../manuscript/tables/raw_wilcox.tex")
print(xtable(table_out, caption = table_caption), include.rownames = FALSE)
sink()
```

@@

## Save
sink(file = "../manuscript/tables/raw_wilcox_appendix.tex")
print(xtable(table_out, caption = table_caption), include.rownames = FALSE)
sink()
```

These tables are LaTeX format and can be added into documents after a small amount of manipulation.
